%% This document requires the class "ChaseCV" which is included in the attached file as "ChaseCV.cls"
%% This CV format was editied and modified from the template and class developed by Nicola Fontana <ntd at entidi.it>
%% and distributed under the terms of the LaTeX Project Public License


\documentclass[fontsize=8pt]{ChaseCV}
\usepackage[english]{babel}

\newcommand\PERSONAL{%
\personal
    {920 E. 61st Street, Apt. 1\newline Chicago, IL 60637}
    {(561) 436 8295}
    {cocorbin@uchicago.edu}}


\begin{document}

\part{C H A S E \quad O W E N \quad C O R B I N}

\section{Education}

\begin{eventlist}

\item{\textit{Fall 2014 - Summer 2014}}
	{\textbf{The University of Chicago}}
	{MA -- Program in Social Sciences}

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\textit{Coursework:} \\
\textbullet{} Economics: Human Capital, Family Economics, \\
Inequality and Social Interactions, Computational Economics \\
\textbullet{} Math: Probability, Statistical Inference, Linear Algebra \\
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\

\item{\textit{Summer 2013}}
	{\textbf{University of California - Berkeley}}
	{Post Baccalaureate Study}

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\textit{Coursework:} \\
\textbullet{}Behavioral Economics, Psychology and Economics \\
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\

\item{\textit{Fall 2008 - Fall 2013}}
	{\textbf{University of Florida}}
	{BA --  Economics (\textit{Summa Cum Laude}) \\
	BA -- Philosophy(\textit{Cum Laude})}

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\textit{Coursework:} \\
\textbullet{} Economics: Microeconomics (I-II), Macro. (I-II) \\
Game Theory, Econometrics, Information Economics (grad) \\
\textbullet{} Math: Calculus(I-III), Differential Equations, Statistics \\
\textbullet{} Philosophy: Moral Phil. (I-III), Applied Ethics (I-III) \\
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\end{eventlist}

\section{Research Experience}

\begin{eventlist}

\item{\textbf{July 2014 -- Current}}
	{Research Assistant / Statistical Analyst}
	{\textit{The Scenes Project at UChicago} \\
	Principal Investigator: \\
	Terry N. Clark, PhD}

\textbullet{} Lead RA for all statistical and programming projects \\
\textbullet{} Oversee three reportees; train and assign weekly tasks. \\
\textbullet{} Analysis of large international business and demographic datasets \\

\item{\textbf{October 2014 -- Current}}
     {Research Assistant}
     {\textit{Gift Exchange Field Experiment} \\
     Principal Investigators: \\
     John List, PhD and Stefano DellaVigna, PhD}

\textbullet{} Responsible for supervising experimental subjects, \\
implementing research design, and recording data \\

\item{\textbf{Independent Research}}
	{\textit{Grad:} Master's Thesis}
	{\textit{Undergrad:} Senior Thesis \\
	University Scholar's Project}
	
-------------------------------------------------------------------------------- \\
\textit{MA Thesis:} Investigating Returns to School Quality \\
for a Sample of Academic Researchers \\
\textit{Faculty Reader:} James J. Heckman, PhD \\
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\textit{Senior Thesis:} Relating Theories of Inductive \\
Reasoning to Decisions Under Uncertainty \\
\textit{Faculty Reader:} David Denslow, PhD \\
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - \\
\textit{University Scholars Project:} Negative Effects of \\
Public Institution Lending Policies on the Florida \\
Condominum Project \\
\textit{Faculty Reader:} David Denslow, PhD \\
-------------------------------------------------------------------------------- \\

\end{eventlist}

\ifjob{}{}{\PERSONAL}

\section{Teaching and Internship Experience}

\begin{yearlist}

\item[The Princeton Review]{Jan. 2014 -- Current}
     {Content Developer}
     {National Operations}
     
\item[The Princeton Review]{Aug. 2013 -- July 2014}
	{Master Tutor}
	{Berkeley, CA Operations}

\item[The Princeton Review]{Apr. 2009 -- Feb. 2012}
	{Classroom Teacher}
	{Gainesville, FL Operations}
    

\item[Sylvan Learning Centers]{January 2012 - June 2012}
     {Advanced Math Teacher}
     {Lantana, FL}
     
\item{- - - - - - - - - - - - -}
{- - - - - - - - - - - - -}
{}

\item[Legal Aid Society of Palm Beach County]{Apr. 2010 - Sep. 2010}
     {Project Intern}
     {West Palm Beach, FL}

\item[The O.E.C.D]{Jun. 2009 -- May 2010}
	{Student Ambassador}
	{Gainesville, FL}
    
\end{yearlist}

\section{Programming and Software Skills}

\begin{factlist}
\item{Java}   {Web Scraping, Data Mining, Information Extraction, Package Development}
\item{Python}   {Numerical Analysis, Object Oriented Programming, Data Mining, Package Development, Statistical Analysis, Parallelization}
\item{Julia} {Numerical Analysis, Statistical Analysis, Functional Programming, Parallelization}
\item{HTML} {Web Development, Web Design, Content Development, CSS manipulation}
\item{Software}{Stata, Spss, MS Office, Adobe Creative Suite}
\item{Other} {LaTeX, RegEx, mySQL, Linux}
\end{factlist}

\section{Awards and Honors}

\begin{factlist}

\item{University Merit Scholarship}
     {The University of Chicago}

\item{Best Undergraduate Research Paper}
     {The University of Florida}
     
\item{University Scholar (Research Grant)}
     {The University of Florida}

\item{Anderson Scholar (Top 3\% of Class}
	{The University of Florida}
	
\item{Truman Scholarship Nominee}
	{The University of Florida}	

\end{factlist}

\end{document}
